Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-16 doc/GMP2015/revision_1/s07_pinnedline.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.

\begin{figure}
\centering

\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
  \caption{}
  \label{fig:cellulose}
\end{subfigure}
\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=\linewidth]{img/crosslink}
  \caption{}
  \label{fig:crosslink}
\end{subfigure}%
\caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (b) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
\end{figure}

@@

The cross-linking microfibrils can be modeled as a pinned line-
incidence constraint system in $\mathbb{R}^2$, where incidence
constraints are used instead of distance constraints.

@@

\begin{figure}
  \centering
   \includegraphics[width=.7\linewidth]{img/pinned}
\caption{ An isostatic pinned line-incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

Theorem~\ref{theorem:main}
holds for  pinned line-incidence graphs with the above modified definition.
The proof is similar to the original proof (in the Appendix) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

@@

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs. The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned
line-incidence graphs is given in Appendix~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main}
to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

\noindent
\note The recombination problem for  pinned line-incidence systems is trivial.
Since the pins are given fixed positions in the plane,
the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.

>>>>

% \begin{figure}
% \centering

% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
%   \caption{}
%   \label{fig:cellulose}
% \end{subfigure}
% \begin{subfigure}{.49\linewidth}
%   \centering
%   \includegraphics[width=\linewidth]{img/crosslink}
%   \caption{}
%   \label{fig:crosslink}
% \end{subfigure}%
% \caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (b) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
% \end{figure}

\ClearMyMinHeight
\SetMyMinHeight{.45}{img/AFM_Innventia_nanocellulose}
\SetMyMinHeight{.45}{img/crosslink}

\begin{figure}\centering%
    %
    \begin{subfigure}{0.45\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
        \caption{}\label{fig:cellulose}
    \end{subfigure}%
    %
    \hfill
    \begin{subfigure}{0.45\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/crosslink}
        \caption{}\label{fig:crosslink}
    \end{subfigure}%
    %
    \caption{(\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (\ref{fig:crosslink}) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
\end{figure}%

@@

The cross-linking microfibrils can be modeled as a pinned line-incidence constraint system in $\mathbb{R}^2$, where incidence constraints are used instead of distance constraints.

@@

\begin{figure}\centering
    \includegraphics[width=.7\linewidth]{img/pinned}
    \caption{An isostatic pinned line-incidence graph.}
    \label{fig:pinned_line}
\end{figure}

@@

Theorem~\ref{theorem:main} holds for  pinned line-incidence graphs with the above modified definition. The proof is similar to the original proof (in \ref{theorem:main:proof}) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

@@

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs. The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs is given in~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main} to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

% \noindent
% \note The recombination problem for  pinned line-incidence systems is trivial. Since the pins are given fixed positions in the plane, the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.

\sidenote{The recombination problem for  pinned line-incidence systems is trivial. Since the pins are given fixed positions in the plane, the solutions of a isostatic sub-system will automatically be consistent with solutions of the remaining of the system.}
